Inferring probabilistic stellar rotation periods using Gaussian processes

### 2017-02-16 documents/ms.tex
adding paragraph about tel aviv results and RMS values

@@

@@

\begin{table*}
\begin{center}
    \caption{Median absolute (MAD) and median relative (MRD) deviations for
    the LS periodogram, ACF and GP period recovery methods.}
\begin{tabular}{lccc}
Method & MAD & MRD \\
    \hline
    LS periodogram & \pgramMAD\ days & \percentpgramMAD \% \\
    ACF & \acfMAD\ days & \percentacfMAD \% \\
    GP (uninformative prior) & \gpMADnp\ days & \percentgpMADnp \% \\
    GP (acf prior) & \gpMAD\ days & \percentgpMAD \% \\
\end{tabular}
\end{center}
\end{table*}
\label{tab:MADs}

>>>>

\newcommand{\lntelavivMAD}{0.02}
\newcommand{\telavivMAD}{0.34}
\newcommand{\percenttelavivMAD}{1.75}

\newcommand{\acfRMS}{1.75}
\newcommand{\telavivRMS}{25.09}
\newcommand{\pgramRMS}{19.50}
\newcommand{\gpRMSnp}{7.48}
\newcommand{\gpRMS}{7.12}

@@

We also compare our results to those of the Tel Aviv team in
\citet{Aigrain2015} who use the ACF method described in \citet{Mcquillan2013}.
Although we follow the same overall ACF method in this paper, the exact
implementation of \citet{Mcquillan2013} code is slightly different and
therefore produces different results.
The MRD of their results relative to the true rotation periods is
\percenttelavivMAD\% which is smaller than the results produced by the GP
method: their results are more precise.
However, they produce a larger number of large outliers --- they predict
periods that are significantly different from the true period in more cases
than the GP method.
This is revealed by comparing the root-mean-squared (RMS) of the two sets of
results, which is more sensitive to outliers: the RMS of the Tel Aviv results
is 25 days and the RMS of GP results is 7 days.
The Tel Aviv ACF results are therefore more precise but are catastrophically
wrong in a larger number of cases.
% This can be understood as a consequence of the ACF method's sensitivity to
% noise.
% The ACF method will predict a period according to the positions of the highest
% peaks in the ACF which, on occasion, are produced by noise in the data rather
% than the periodic signal.
% On the other hand, the priors on the GP parameters ensure that a `reasonable'
% rotation period is always recovered --- it is therefore less sensitive to
% noise and rarely infers periods that are .

@@

\begin{table*}
\begin{center}
    \caption{Median absolute (MAD), median relative (MRD) deviations and
    root-mean-squared (RMS) for
    the LS periodogram, ACF, \citet{Mcquillan2013} ACF and GP period recovery
    methods.}
\begin{tabular}{lcccc}
    Method & MAD & MRD & RMS \\
    \hline
    LS periodogram & \pgramMAD\ days & \percentpgramMAD \% & \pgramRMS\ days\\
    ACF & \acfMAD\ days & \percentacfMAD \% & \acfRMS\ days \\
    ACF \citep{Mcquillan2013} & \telavivMAD\ days & \percenttelavivMAD \%
    & \telavivRMS\ days \\
    GP (uninformative prior) & \gpMADnp\ days & \percentgpMADnp \% &
    \gpRMSnp\ days \\
    GP (acf prior) & \gpMAD\ days & \percentgpMAD \% & \gpRMS\ days \\
\end{tabular}
\end{center}
\end{table*}
\label{tab:MADs}
